Initial Analysis

### 2019-09-17 Initial_Analysis.Rmd
Figure out issues with Russia (Finally!)

# Load neighbours data from previouse routine
Neighbours_Data <- fread(paste(Data_Path,"Spatial_Data/EEZ_Neighbours_List.csv", sep =""))

@@

Spp <- 600423 #This species should work

>>>>

# Load neighbours data from previouse routine
Neighbours_Data <- read_excel(paste(Data_Path,"Spatial_Data/EEZ_Neighbours_List.xlsx", sep =""))

# Modifications have to be made if ran un Hall
# R<e9>union (Réunion) and C<f4>te d'Ivoire (Côte d'Ivoire)

@@

# Spp <- 600423 #This species should work

# Its a problem with compabillity between Windows and MAC. Fixed by changing the neighbours csv. to excell

# Now Check Vietnam...Curacao and Réunion...
# In INDEXES "Vietnam" in all others "Viet Nam"
# Fixed directly on the excell

# The russioan probelmo

# Load neighbours data from previouse routine
Neighbours_Data <- read_excel(paste(Data_Path,"Spatial_Data/EEZ_Neighbour_List.xlsx", sep =""))

EEZCellIUD913 <- EEZ_CellID %>% 
  filter(EEZID == 913)

R912 <- Neighbours_Data %>% 
  filter(ID == 912)

R913 <- Neighbours_Data %>% 
  filter(ID == 913)

anti_join(R912,R913)

Index_Code913 <- Index_Code %>% 
  filter(EEZID == 913)

Neighbours_Data %>% 
  filter(INDEX %in% Index_Code913$INDEX)

# SAU relations between INDEX and Country's EEZs
EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
# EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_JEPA_92019.xlsx",sep=""))
EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
# EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_JEPA_92019.xlsx",sep=""))
colnames(EEZ_CellID) <- c("EEZID","INDEX")

x <- Neighbours_Data %>%
  select(-Neighbour) %>% 
  group_by(Territory) %>% 
  distinct() %>% 
  anti_join(Index_Code) %>% 
  group_by(Territory) %>% 
  summarise(n());x

# World_sf %>% 
#   filter(Territory %in% x$Territory)

# Fuck it! Re-run Neighbours code...

Russians <- c("Russia (Laptev to Chukchi Sea)", #913
              "US Virgin Islands") #912

SF_Names <- 850

Russian_Index <- Index_Code %>% 
  filter(Territory %in% Russians)

unique(Russian_Index$EEZID)
unique(Russian_Index$Territory)

World_sf %>% 
  # filter(Territory == "Russia (Laptev to Chukchi Sea)") # EEZid 912
  # filter(Territory == "Russia (Kara Sea)") # EEZid also 912
  filter(Territory %in% Russians) %>% 
  ggplot() +
  geom_sf(aes(fill = Territory))

unique(Russian_sf$Territory)

# split shapefile by DF
 Russian_id <- World_sf %>% 
  filter(Territory %in% Russians) %>% 
  left_join(Russian_Index, by= "Territory") %>%  
  mutate(EEZID = ifelse(Territory == "Russia (Kara Sea)",912,913)) %>% 
  filter(EEZID == 913) %>% 
  st_simplify(preserveTopology = TRUE, dTolerance = 1000)

 ggplot(Russian_id) +
   geom_sf(aes())

 # ok!

# split shapefile by DF
Russia_id_912_913 <- World_sf %>% 
  filter(Territory %in% Russians) %>% 
  left_join(Russian_Index, by= "Territory") %>%  
  mutate(EEZID = ifelse(Territory == "Russia (Kara Sea)",912,913)) %>% 
  as.data.frame() %>% 
  ungroup() %>% 
  select(Territory,INDEX,EEZID)

write.csv(Russia_id_912_913,
         "Russia_id_912_913.csv",
         row.names = F)

head(x)
